% !TeX program = lualatex

\documentclass{wgu-cv}

\yourname{William G Underwood}
\youraddress{
  ORFE Department,
  Sherrerd Hall,
  Charlton Street,
  Princeton,
  NJ 08544,
  USA
}
\youremail{wgu2@princeton.edu}
\yourwebsite{wgunderwood.github.io}

\begin{document}

\maketitle

\section{Employment}

\subsection{Postdoctoral Research Associate in Statistics}
{Jul 2024 -- Jul 2026}
\subsubsection{University of Cambridge}

\begin{itemize}
  \item Advisor: Richard Samworth,
    Department of Pure Mathematics and Mathematical Statistics
  \item Funding: European Research Council Advanced Grant 101019498
\end{itemize}

\subsection{Assistant in Instruction}
{Sep 2020 -- May 2024}
\subsubsection{Princeton University}

\begin{itemize}

  \item
    ORF 499:
    Senior Thesis,
    Spring 2024

  \item
    ORF 498:
    Senior Independent Research Foundations,
    Fall 2023

  \item
    SML 201:
    Introduction to Data Science,
    Fall 2023

  \item
    ORF 363:
    Computing and Optimization,
    Spring 2023, Fall 2020

  \item
    ORF 524:
    Statistical Theory and Methods,
    Fall 2022, Fall 2021

  \item
    ORF 526:
    Probability Theory,
    Fall 2022

  \item
    ORF 245:
    Fundamentals of Statistics,
    Spring 2021

\end{itemize}

\section{Education}

\subsection{PhD in Operations Research \& Financial Engineering}
{Sep 2019 -- May 2024}
\subsubsection{Princeton University}

\begin{itemize}
  \item Dissertation:
    Estimation and Inference in Modern Nonparametric Statistics
  \item Advisor:
    Matias Cattaneo, Department of Operations Research \& Financial Engineering
\end{itemize}

\subsection{MA in Operations Research \& Financial Engineering}
{Sep 2019 -- Sep 2021}
\subsubsection{Princeton University}

\subsection{MMath in Mathematics \& Statistics}
{Oct 2015 -- Jun 2019}
\subsubsection{University of Oxford}

\begin{itemize}
  \item Dissertation:
    Motif-Based Spectral Clustering of Weighted Directed Networks
  \item Supervisor:
    Mihai Cucuringu,
    Department of Statistics
\end{itemize}

\section{Research \& publications}

\subsection{Articles}{}
\begin{itemize}

  \item Uniform inference for kernel density estimators with dyadic data,
    with M D Cattaneo and Y Feng.
    \emph{Journal of the American Statistical Association}, forthcoming, 2024.
    \arxiv{2201.05967}.

  \item Motif-based spectral clustering of weighted directed networks,
    with A Elliott and M Cucuringu.
    \emph{Applied Network Science}, 5(62), 2020.
    \arxiv{2004.01293}.

  \item Simple Poisson PCA: an algorithm for (sparse) feature extraction
    with simultaneous dimension determination,
    with L Smallman and A Artemiou.
    \emph{Computational Statistics}, 35:559--577, 2019.

\end{itemize}

\subsection{Preprints}{}
\begin{itemize}

  \item Inference with Mondrian random forests,
    with M D Cattaneo and J M Klusowski, 2023. \\
    \arxiv{2310.09702}.

  \item Yurinskii's coupling for martingales,
    with M D Cattaneo and R P Masini.
    \emph{Annals of Statistics}, reject and resubmit, 2023.
    \arxiv{2210.00362}.

\end{itemize}

\pagebreak

\subsection{Works in progress}{}
\begin{itemize}

  \item Higher-order extensions to the Lindeberg method,
    with M D Cattaneo and R P Masini.

  \item Adaptive Mondrian random forests,
    with M D Cattaneo, R Chandak and J M Klusowski.
\end{itemize}

\subsection{Presentations}{}
\begin{itemize}

  \item Statistics Seminar, University of Pittsburgh, February 2024
  \item Statistics Seminar, University of Illinois, January 2024
  \item Statistics Seminar, University of Michigan, January 2024
  \item PhD Poster Session, Two Sigma Investments, July 2023
  \item Research Symposium, Two Sigma Investments, June 2022
  \item Statistics Laboratory, Princeton University, September 2021
\end{itemize}

\subsection{Software}{}
\begin{itemize}

  \item MondrianForests: Mondrian random forests in Julia, 2023. \\
    \github{wgunderwood/MondrianForests.jl}

  \item DyadicKDE: dyadic kernel density estimation in Julia, 2022. \\
    \github{wgunderwood/DyadicKDE.jl}

  \item motifcluster: motif-based spectral clustering
    in R, Python and Julia, 2020. \\
    \github{wgunderwood/motifcluster}

\end{itemize}

\section{Awards \& funding}
\vspace{-0.22cm}

\begin{itemize}
  \item School of Engineering and Applied Science Award for Excellence,
    Princeton University
    \hfill 2022%
  \item Francis Robbins Upton Fellowship in Engineering,
    Princeton University
    \hfill 2019%
  \item Royal Statistical Society Prize,
    Royal Statistical Society \& University of Oxford
    \hfill 2019%
  \item Gibbs Statistics Prize,
    University of Oxford
    \hfill 2019%
  \item James Fund for Mathematics Research Grant,
    St John's College, University of Oxford
    \hfill 2017%
  \item Casberd Scholarship,
    St John's College, University of Oxford
    \hfill 2016%
\end{itemize}

\section{Professional experience}

\subsection{Quantitative Research Intern}
{Jun 2023 -- Aug 2023}
\subsubsection{Two Sigma Investments}
\vspace{-0.20cm}

\subsection{Machine Learning Consultant}
{Oct 2018 -- Nov 2018}
\subsubsection{Mercury Digital Assets}
\vspace{-0.18cm}

\subsection{Educational Consultant}
{Feb 2018 -- Sep 2018}
\subsubsection{Polaris \& Dawn}
\vspace{-0.20cm}

\subsection{Premium Tutor}
{Feb 2016 -- Oct 2018}
\subsubsection{MyTutor}
\vspace{-0.20cm}

\subsection{Statistics \& Machine Learning Researcher}
{Aug 2017 -- Sep 2017}
\subsubsection{Cardiff University}
\vspace{-0.20cm}

\subsection{Data Science Intern}
{Jun 2017 -- Aug 2017}
\subsubsection{Rolls-Royce}
\vspace{-0.20cm}

\subsection{Peer review}{}

\emph{Econometric Theory,
  Journal of the American Statistical Association,
  Journal of Business \& Economic Statistics,
  Journal of Causal Inference,
  Journal of Econometrics,
Operations Research.}

\section{References}
\vspace{-0.22cm}

\begin{itemize}

  \item
    Matias Cattaneo,
    Professor,
    ORFE,
    Princeton University

  \item
    Jason Klusowski,
    Assistant Professor,
    ORFE,
    Princeton University

  \item
    Jianqing Fan,
    Professor,
    ORFE,
    Princeton University

  \item
    Ricardo Masini,
    Assistant Professor,
    Statistics,
    University of California, Davis

\end{itemize}

\end{document}
