\documentclass{article}

\begin{document}

% no comment
This line is too long because it has more than eighty characters inside it. Therefore it should be split.

% break before comment
This line is too long because it has more than eighty characters inside it. Therefore it % should be split.

% break after spaced comment
This line is too long because it has more than % eighty characters inside it. Therefore it should be split.

% break after non-spaced comment
This line is too long because it has more than% eighty characters inside it. Therefore it should be split.

% unbreakable line
Thislineistoolongbecauseithasmorethan%eightycharactersinsideit.Buttherearenospacessoitcannotbesplit.

% line can be broken after 80 chars
Thislineistoolongbecauseithasmorethaneightycharactersinsideitandtherearenospacesuntillater where there are some spaces so we can split this line here

% long line only after indenting
(
1234567890 1234567890 1234567890 1234567890 1234567890 1234567890 1234567890 123
)

% double break after comment
This line has a long comment. % This comment is very long so needs to be split over three lines which is another edge case which should be checked here with all these extra words

% double break after only comment
% This line is all a long comment. This comment is very long so needs to be split over three lines which is another edge case which should be checked here with all these extra words

% lines containing \<space>
This line would usually be split at the special character part with a slash\ but it's best to break the line earlier.

% long lines with brackets
(This line is too long because it has more than eighty characters inside it. Therefore it should be split. It also needs splitting onto multiple lines, and the middle lines should be indented due to these brackets.)

% long lines with double brackets
((This line is too long because it has more than eighty characters inside it. Therefore it should be split. It also needs splitting onto multiple lines, and the middle lines should be doubly indented due to these brackets.))

\end{document}
